Enforced Invariant Confluence

### 2020-01-13 doc/the_vldb_journal_paper/sections/invariant_confluence.tex
Minor invariant confluence section changes.
- Clarified that the merge operator doesn't need any special properties.
- Fixed the formatting. For some weird reason, equations in \[\] are not
  being centered. I have no idea why. I added \hfills to fix it though.
  A little jank, but oh well.

Note that by modelling a transaction $t$ as a function $S \to S$, we focus
exclusively on the effects that a transaction has on the object (i.e.\
``writes'' to the object). Transactions are also free to read the value of the
object, but these reads are not captured by our model because, as we'll see,
they do not affect \invariantconfluence{}. For example, we could model any
read-only transaction as a function $t$ where $t(s) = s$ for every $s \in S$.

@@

\subsection{Expression-Based Formalism}
To define \invariantconfluence{} formally, we represent a state produced by a
system execution as a simple expression generated by the grammar
\[
  e ::= s \mid t(e) \mid e_1 \join e_2
\]
where $s$ represents a state in $S$ and $t$ represents a transaction in $T$. As
an example, consider the system execution in \figref{SystemExecution} in which
a distributed object is replicated across servers $p_1$, $p_2$, and $p_3$.
Server $p_3$ begins with state $s_0$, transitions to state $s_2$ by executing
transaction $u$, transitions to state $s_5$ by executing transaction $w$, and
then transitions to state $s_7$ by merging with server $p_1$. Similarly, server
$p_1$ ends up with state $s_6$ after executing transactions $t$ and $v$ and
merging with server $p_2$. In \figref{Expression}, we see the abstract syntax
tree of the corresponding expression for state $s_7$.

@@

Finally, we say $O$ is \defword{\invariantconfluent} with respect to $s_0$,
$T$, and $I$, abbreviated \defword{\sTIconfluent{}}, if all reachable states
satisfy the invariant:
\[
  \setst{s \in S}{\sTIreachablepredicate{s}} \subseteq I
\]

>>>>

Note that we do not assume any properties of $\join$, like associativity or
commutativity. Also note that by modelling a transaction $t$ as a function $S
\to S$, we focus exclusively on the effects that a transaction has on the
object (i.e.\ ``writes'' to the object). Transactions are also free to read the
value of the object, but these reads are not captured by our model because, as
we'll see, they do not affect \invariantconfluence{}. For example, we could
model any read-only transaction as a function $t$ where $t(s) = s$ for every $s
\in S$.

@@

\subsection{Expression-Based Formalism}
To define \invariantconfluence{} formally, we represent a state produced by a
system execution as a simple expression generated by the grammar
%
\[
  \hfill
  e ::= s \mid t(e) \mid e_1 \join e_2
  \hfill
\]
%
where $s$ represents a state in $S$ and $t$ represents a transaction in $T$. As
an example, consider the system execution in \figref{SystemExecution} in which
a distributed object is replicated across servers $p_1$, $p_2$, and $p_3$.
Server $p_3$ begins with state $s_0$, transitions to state $s_2$ by executing
transaction $u$, transitions to state $s_5$ by executing transaction $w$, and
then transitions to state $s_7$ by merging with server $p_1$. Similarly, server
$p_1$ ends up with state $s_6$ after executing transactions $t$ and $v$ and
merging with server $p_2$. In \figref{Expression}, we see the abstract syntax
tree of the corresponding expression for state $s_7$.

@@

Finally, we say $O$ is \defword{\invariantconfluent} with respect to $s_0$,
$T$, and $I$, abbreviated \defword{\sTIconfluent{}}, if all reachable states
satisfy the invariant:
\[
  \hfill
  \setst{s \in S}{\sTIreachablepredicate{s}} \subseteq I
  \hfill
\]
